---
title: "Main text figures"
author: "Erin Macartney, Szymek Drobniak, Shinichi Nakagawa, Malgorzata Lagisz"
output: 
    rmdformats::readthedown:
      code_folding: hide
      code_download: true
      toc_depth: 4
editor_options: 
  chunk_output_type: console
---

    
```{r, include = FALSE}
knitr::opts_chunk$set(
message = FALSE,
warning = FALSE,
cache = TRUE, 
tidy = TRUE, 
echo = TRUE
)

rm(list = ls())
```

### Seutup and data organisation

```{r setup, results = 'hide'}

knitr::opts_chunk$set(echo = TRUE)

library(readxl)
library(plyr)
library(here)
library(tibble)
library(dplyr)
library(tidyverse)
library(stringr)
library(knitr)
library(forcats)
library(ggplot2)
library(hrbrthemes) #for ggplot2
library(bibliometrix)
library(igraph)
library(patchwork)
library(RColorBrewer)
library(rotl) #for getting OTTIDs from OTL
library(phytools) #for plotting trees
library(timetree) #can create trees with branch lengths
library(ape)
```

``` {r, results = 'hide'}
#manually extracted data
xldata <- "./Data_extraction_postcrosschecking.xlsx"
# xldata <- read_excel(here(Data_extraction_postcrosschecking.xlsx"))

# #bibliometric data
# bib <- convert2df("./bibliometric.bib", dbsource = "scopus", format = "bibtex")
bib <- convert2df(here("bibliometric.bib"), dbsource = "scopus", format = "bibtex")
```


``` {r, results = 'hide'}
#Splitting list of tabs into separate dataframes
excel_sheets(path = xldata)
tab_names <- excel_sheets(path = xldata)


#creating a list of dataframes per tab
list_all <- lapply(tab_names, function(x) read_excel(path = xldata, sheet = x))

#assigning tab names to each dataframe
names(list_all) <- tab_names

#get dataframes out of list
list2env(list_all, .GlobalEnv)
```

# Within and between discipline research patterns 

Fig.1 is the diagram showing the difference between inter- and trans-generational effects and Fig. 2 is the ROSES diagram which were not created on R. 

## Figure 3 - Disciplines and year published {.tabset}

### Fig. 3A - SR with Disciplines

Still todo is to write desciptions of each figure

``` {r, results = 'hide'}

count_discipline <-Review_info %>% count(discipline_code) %>% arrange(desc(n)) 
percent_discipline <- count_discipline %>% mutate(percent = (n/sum(n))*100)
percent_discipline$percent <- round(percent_discipline$percent, digits = 0)
percent_discipline$discipline_code <- factor(percent_discipline$discipline_code, level = percent_discipline$discipline_code[order(percent_discipline$n, decreasing = TRUE)])

brewer.pal(6, "Accent") # matching colours of disciplines from brewer used in other figs
my.cols <- (c("#BEAED4","#FFFF99" ,"#386CB0","#7FC97F","#FDC086","#F0027F"))

Fig3a <- ggplot(percent_discipline, aes(x = discipline_code, y = percent)) + 
  geom_col(aes(fill = discipline_code), width = 0.7) + 
  geom_text(aes(label = percent), hjust = -0.2) +
  coord_flip() + 
  scale_y_continuous(name = "Percent (%)") +
  xlab("Discipline") + 
  scale_fill_manual(values=my.cols) +
  theme_classic() +
  theme(legend.position = "none")

Fig3a

```

### Fig. 3B - Year published

``` {r}

Publication_info_discipline <- merge(Publication_info, Review_info)

Fig3b <- Publication_info_discipline %>% 
  count(year, discipline_code) %>%
  ggplot(aes(x = year, y = n)) +
  geom_col(aes(, fill = discipline_code), width = 0.7) +
  xlim(2009, 2021.5) +
  ylim(0, 14.5) +
  geom_text(position = position_stack(vjust = 0.5), aes(fill = discipline_code, label = n)) +
  theme_classic() +
  scale_fill_brewer(palette = "Accent") +
  labs(x = "Year", y = "Article count", fill = "Discipline")+
  theme(legend.position = "none", axis.title.x = element_text(size = 10))



Fig3b

```


### Fig. 3 - Panel

``` {r}
Fig3 <- Fig3a +  Fig3b + plot_annotation(tag_levels = "A")

Fig3 
```

## Figure 4 - Inter vs Trans gen effects including mode of transmission and term use {.tabset}

### Fig. 4A - Inter vs Trans

``` {r}
Merged_inter_vs_trans <- merge(Inter_vs_trans_info, Review_info)

count_inter_vs_trans <- Merged_inter_vs_trans %>% count(inter_vs_trans_code, by = discipline_code ) %>% arrange(desc(n))
percent_inter_vs_trans <- count_inter_vs_trans %>% mutate(percent = (n/sum(n))*100)
percent_inter_vs_trans$percent <- round(percent_inter_vs_trans$percent, digits = 0)

percent_inter_vs_trans <-percent_inter_vs_trans %>%
  rename(
    discipline_code = by
  )

Fig4a <- ggplot(percent_inter_vs_trans, aes(x = inter_vs_trans_code, y = percent)) + 
  geom_col(aes(fill = discipline_code), width = 0.7) +
  coord_flip() + 
  scale_y_continuous(name = "Percent (%)") +
  ylim(0,80)+
  geom_text(position = position_stack(vjust = 0.5), aes(fill = discipline_code, label = percent)) +
  theme_classic() +
  scale_fill_brewer(palette = "Accent") +
  labs(x = "Inter- vs trans-inheritnace", fill = "Discipline")+
  theme(legend.position = "none")

Fig4a

#TODO cant figure out how to add text on top of bar of total percent

```

### Fig.4B - Transmission mode 

```{r}

Merged_transmission_info <- merge(Transmission_info, Review_info)

count_transmission <- Merged_transmission_info %>%  count(transmission_code, by = discipline_code) %>% arrange(desc(n))
percent_transmission <- count_transmission %>% mutate(percent = (n/sum(n))*100)
percent_transmission$percent <- round(percent_transmission$percent, digits = 0)
percent_transmission <-percent_transmission %>%
  rename(
    discipline_code = by
  )

Fig4b <- ggplot(percent_transmission, aes(x = transmission_code, y = percent)) + 
  geom_col(aes(fill = discipline_code), width = 0.7) +
  coord_flip() + 
  scale_y_continuous(name = "Percent (%)") +
  geom_text(position = position_stack(vjust = 0.5), aes(fill = discipline_code, label = percent)) +
  theme_classic() +
  scale_fill_brewer(palette = "Accent") +
  labs(x = "Transmission mode", fill = "Discipline") +
  theme(legend.position = "none")

Fig4b

```

### Fig. 4C - Match vs mismatch inter- vs trans- definition

``` {r}
count_terminology <- Review_info %>% count(terminology_code, by = discipline_code) %>% arrange(desc(n))
percent_terminology <- count_terminology %>% mutate(percent = (n/sum(n))*100)
percent_terminology$percent<-round(percent_terminology$percent, digits = 0)

percent_terminology<- percent_terminology %>%
  rename(
    discipline_code = by
  )

Fig4c <- ggplot(percent_terminology, aes(x = reorder(terminology_code, -percent), y = percent)) + 
  geom_col(aes(fill = discipline_code), width = 0.7) + 
  coord_flip() + 
  scale_y_continuous(name = "Percent (%)") +
  geom_text(position = position_stack(vjust = 0.5), aes(fill = discipline_code, label = percent)) +
  theme_classic() +
  scale_fill_brewer(palette = "Accent") +
  labs(x = "Terminology use matches Fig. 1", fill = "Discipline")+
  theme(legend.position = "none")


Fig4c
```

### Fig. 4 - Panel

``` {r}
Fig4 <- (Fig4a / Fig4b /Fig4c) + plot_annotation(tag_levels = "A")

Fig4 

# TODO how to get total percents at the top of each bar as well as within each bar?
```



``` {r}

##Supplementary figure

#Inter_vs_trans_transmision <- merge(Merged_inter_vs_trans, Transmission_info)
# 
# 
# count_inter_vs_trans_transmission <- Inter_vs_trans_transmision %>% count(inter_vs_trans_code, by = transmission_code) %>% arrange(desc(n))
# percent_inter_vs_trans_transmission <- count_inter_vs_trans_transmission %>% mutate(percent = (n/sum(n))*100)
# percent_inter_vs_trans_transmission$percent <- round(percent_inter_vs_trans_transmission$percent, digits = 0)
# 
# percent_inter_vs_trans_transmission <-percent_inter_vs_trans_transmission %>%
#   rename(
#     transmission_code = by
#   )
# 
# Fig5 <- ggplot(percent_inter_vs_trans_transmission, aes(x = inter_vs_trans_code, y = percent)) + 
#   geom_col(aes(fill = transmission_code), width = 0.7) + 
#   coord_flip() + 
#   scale_y_continuous(name = "Percent (%)") +
#   geom_text(position = position_stack(vjust = 0.5), aes(fill = transmission_code, label = percent)) +
#   theme_classic() +
#   scale_fill_brewer(palette = "Accent") +
#   labs(x = "Inter- vs trans-inheritnace", fill = "Transmission mode")+
#   theme(legend.position = "none")
# 
# Fig5
# 
# #TODO should we remove all of the unclear datapoints?
```



```{r}
#supplementary figure

### Descendant generations within and between disciplines
# 
# merged_descendant_generat <- merge(Descendant_generat_info, Review_info)
# 
# count_descendant_generat <- merged_descendant_generat %>% count(descendant_generat_code, by = discipline_code) %>% arrange(desc(n))
# percent_descendant_generat <- count_descendant_generat %>% mutate(percent = (n/sum(n))*100)
# 
# percent_descendant_generat <- percent_descendant_generat %>% 
#   rename (
#     discipline_code = by
#   )
# 
# ggplot(percent_descendant_generat, aes(x = descendant_generat_code, y = percent)) + 
#   geom_col(aes(fill = transmission_code), width = 0.7) + 
#   theme_light() +
#   coord_flip() + 
#   scale_y_continuous(name = "Percent (%)") +
#   theme(legend.position = "bottom", axis.title.x = element_text(size = 10), axis.title.y = element_blank()) + 
#   guides(fill=guide_legend(title="Discipline"))

```

## Figure 5 - Ancestor exposures {.tabset}

### Fig. 5A - Timing of exposure
**Note:** We excluded SRs that solely focused on environmental exposures that occured when the F0 generation was a fetus (i.e., pre-natal). However,  some SRs  included primary studies where the F0 generation was exposed pre-natally. This was therefore coded in our data.

```{r}

merged_exposure_timing <- merge(Exposure_timing_info, Review_info)

count_exposure_timing <- merged_exposure_timing %>% count(exposure_timing_code, by = discipline_code) %>% arrange(desc(n))
percent_exposure_timing <- count_exposure_timing %>% mutate(percent = (n/sum(n))*100)
percent_exposure_timing$percent<-round(percent_exposure_timing$percent, digits = 0)

percent_exposure_timing <-percent_exposure_timing %>%
  rename (
    discipline_code = by
  )

Fig5a<- ggplot(percent_exposure_timing, aes(x = exposure_timing_code, y = percent)) + 
  geom_col(aes(fill = discipline_code), width = 0.7) + 
   coord_flip() + 
  scale_y_continuous(name = "Percent (%)") +
  geom_text(position = position_stack(vjust = 0.5), aes(fill = discipline_code, label = percent)) +
  theme_classic() +
  scale_fill_brewer(palette = "Accent") +
  labs(x = "Timing of F0 (ancestor) exposure", fill = "Discipline")+
  theme(legend.position = "none")


Fig5a
```

### Fig. 5B - Descendant generation within F0 timing

```{r}
# merged_exposure_timing_generat <- merge(Exposure_timing_info, Descendant_generat_info)
# 
# count_exposure_timing_generat <- merged_exposure_timing_generat %>% count(exposure_timing_code, by = descendant_generat_code) %>% arrange(desc(n))
# percent_exposure_timing_generat <- count_exposure_timing_generat %>% mutate(percent = (n/sum(n))*100)
# percent_exposure_timing_generat$percent<-round(percent_exposure_timing_generat$percent, digits = 0)
# 
# percent_exposure_timing_generat <-percent_exposure_timing_generat %>%
#   rename (
#     descendant_generat_code = by
#   )
# 
# Fig5c<- ggplot(percent_exposure_timing_generat, aes(x = exposure_timing_code, y = percent)) + 
#   geom_col(aes(fill = descendant_generat_code), width = 0.7) + 
#    coord_flip() + 
#   scale_y_continuous(name = "Percent (%)") +
#   geom_text(position = position_stack(vjust = 0.5), aes(fill = descendant_generat_code, label = percent)) +
#   theme_classic() +
#   scale_fill_brewer(palette = "Greys", direction = -1) +
#   labs(x = "Timing of F0 (ancestor) exposure", fill = "Descendant generation")
# 
# Fig5c


merged_exposure_timing_generat <- merge(Exposure_timing_info, Inter_vs_trans_info)
count_trait_intervstrans <- merged_exposure_timing_generat %>% count(exposure_timing_code, by = inter_vs_trans_code) %>% arrange(desc(n))
percent_exposure_timing_generat <- count_trait_intervstrans  %>% mutate(percent = (n/sum(n))*100)
percent_exposure_timing_generat$percent<-round(percent_exposure_timing_generat$percent, digits = 0)

percent_exposure_timing_generat <- percent_exposure_timing_generat %>%
  rename(
    inter_vs_trans_code = by
           )


Fig5b <- ggplot(percent_exposure_timing_generat, aes(x = exposure_timing_code, y = percent)) + 
  geom_col(aes(fill = inter_vs_trans_code), width = 0.7) + 
   coord_flip() + 
  scale_y_continuous(name = "Percent (%)") +
  geom_text(position = position_stack(vjust = 0.5), aes(fill = inter_vs_trans_code, label = percent)) +
  theme_classic() +
  scale_fill_brewer(palette = "Greys", direction = -1) +
  labs(x = "Timing of F0 (ancestral) exposure", fill = "Inter- vs Trans-generational")

Fig5b

```


### Fig. 5C - Type of environmental exposure

```{r}

merged_F0_env <- merge(F0_env_info, Review_info)
count_F0_env<- merged_F0_env %>% count(F0_env_code, by = discipline_code ) %>% arrange(desc(n))
percent_F0_env <- count_F0_env %>% mutate(percent = (n/sum(n))*100)
percent_F0_env$percent<-round(percent_F0_env$percent, digits = 0)

 
percent_F0_env <-percent_F0_env %>%
  rename(
    discipline_code = by
  )

Fig5c <- ggplot(percent_F0_env, aes(x = F0_env_code, y = percent)) + 
  geom_col(aes(fill = discipline_code), width = 0.7) + 
  coord_flip() + 
  scale_y_continuous(name = "Percent (%)") +
  geom_text(position = position_stack(vjust = 0.5), aes(fill = discipline_code, label = percent)) +
  theme_classic() +
  scale_fill_brewer(palette = "Accent") +
  labs(x = "Type of environmental exposure", fill = "Discipline") + 
  theme(legend.position = "none")
  

Fig5c
```

### Fig. 5D - Environmental effect direction

```{r}

merged_env_eff <- merge(Env_eff_diection_info, Review_info)

count_env_eff <- merged_env_eff %>% count(env_eff_direction_code, by = discipline_code) %>% arrange(desc(n))
percent_env_eff <- count_env_eff %>% mutate(percent = (n/sum(n))*100)
percent_env_eff$percent<-round(percent_env_eff$percent, digits = 0)


percent_env_eff <-percent_env_eff %>%
  rename(
    discipline_code = by
  )

Fig5d <- ggplot(percent_env_eff, aes(x = env_eff_direction_code, y = percent)) + 
  geom_col(aes(fill = discipline_code), width = 0.7) + 
    coord_flip() + 
  scale_y_continuous(name = "Percent (%)") +
  geom_text(position = position_stack(vjust = 0.5), aes(fill = discipline_code, label = percent)) +
  theme_classic() +
  scale_fill_brewer(palette = "Accent") +
  labs(x = "Environmental effect direction", fill = "Discipline") + 
  theme(legend.position = "none")
  
Fig5d

```


### Fig. 5 - Panel

```{r}
Fig5 <- ((Fig5a + Fig5b) / (Fig5c + Fig5d)) + plot_annotation(tag_levels = "A")

Fig5
```

## Figure 6 - Descendant information {.tabset}

### Fig. 6A - Decendant traits

```{r}

merged_descendant_trait <- merge(Descendant_trait_info, Review_info)
count_descendant_trait <- merged_descendant_trait %>% count(descendant_trait_code, by = discipline_code) %>% arrange(desc(n))
percent_descendant_trait <- count_descendant_trait %>% mutate(percent = (n/sum(n))*100)
percent_descendant_trait$percent<-round(percent_descendant_trait$percent, digits = 0)

percent_descendant_trait <- percent_descendant_trait %>%
  rename(
    discipline_code = by
  )

Fig6a<- ggplot(percent_descendant_trait, aes(x = descendant_trait_code, y = percent)) + 
  geom_col(aes(fill = discipline_code), width = 0.7) + 
  coord_flip() + 
  scale_y_continuous(name = "Percent (%)") +
  geom_text(position = position_stack(vjust = 0.5), aes(fill = discipline_code, label = percent)) +
  theme_classic() +
  scale_fill_brewer(palette = "Accent") +
  labs(x = "Descendant traits", fill = "Discipline")+ 
  theme(legend.position = "none")

Fig6a
```

### Fig. 6B - Descendant sex

```{r}

merged_descendant_sex <- merge(Descendant_sex_info, Review_info)
count_descendant_sex <- merged_descendant_sex %>% count(descendant_sex_code, by = discipline_code) %>% arrange(desc(n))
percent_descendant_sex <- count_descendant_sex  %>% mutate(percent = (n/sum(n))*100)
percent_descendant_sex$percent<-round(percent_descendant_sex$percent, digits = 0)

percent_descendant_sex <- percent_descendant_sex %>%
  rename(
    discipline_code = by
           )

Fig6b <- ggplot(percent_descendant_sex, aes(x = descendant_sex_code, y = percent)) + 
  geom_col(aes(fill = discipline_code), width = 0.7) + 
   coord_flip() + 
  scale_y_continuous(name = "Percent (%)") +
  geom_text(position = position_stack(vjust = 0.5), aes(fill = discipline_code, label = percent)) +
  theme_classic() +
  scale_fill_brewer(palette = "Accent") +
  labs(x = "Descendant sex", fill = "Discipline")+ 
  theme(legend.position = "none")

Fig6b

```

### Fig. 6C - Descendant trait grouped by inter- vs trans- 

```{r}
merged_trait_intervstrans <- merge(Descendant_trait_info, Inter_vs_trans_info)
count_trait_intervstrans <- merged_trait_intervstrans %>% count(descendant_trait_code, by = inter_vs_trans_code) %>% arrange(desc(n))
percent_trait_intervstrans <- count_trait_intervstrans  %>% mutate(percent = (n/sum(n))*100)
percent_trait_intervstrans$percent<-round(percent_trait_intervstrans$percent, digits = 0)

percent_trait_intervstrans <- percent_trait_intervstrans %>%
  rename(
    inter_vs_trans_code = by
           )


Fig6c <- ggplot(percent_trait_intervstrans, aes(x = descendant_trait_code, y = percent)) + 
  geom_col(aes(fill = inter_vs_trans_code), width = 0.7) + 
   coord_flip() + 
  scale_y_continuous(name = "Percent (%)") +
  geom_text(position = position_stack(vjust = 0.5), aes(fill = inter_vs_trans_code, label = percent)) +
  theme_classic() +
  scale_fill_brewer(palette = "Greys", direction = -1) +
  labs(x = "Descendant traits", fill = "Inter- vs Trans-generational")

Fig6c

```

### Fig. 6 - Panel

```{r}
Fig6 <- ((Fig6a + Fig6b)/(Fig6c)) + plot_annotation(tag_levels = "A")

Fig6
```

## Species tree
It can't assign OTT to a majority of species

```{r}
# 
# Species_info$species_name<-as.character(Species_info$species_name)
# 
# #checking for species name synonyms
# synons <- tnrs_match_names(unique(Species_info$species_name),  context_name = "Insects")
# 
# synonyms(synons) ## gives list of all synonyms
# synons$ott_id ##gives unique ID number the corresponds to species names in rotl
# synons #tells you how many matches there are
# 
# #making tree
# length(synons$ott_id)
# 
# my.tree <- tol_induced_subtree(ott_ids = synons$ott_id, label_format= "name")
# 
# plot(my.tree, show.tip.label = T, cex = 0.8, no.margin = TRUE) #it's clearly assigning the incorrect taxa names
# 
# intersect(as.character(my.tree$tip.label), Species_info$species_name) ## checking which names are matching 
# 
# setdiff(Species_info$species_name, as.character(my.tree$tip.label)) ## checking which names are not matching 
# 
# in_tree <- is_in_tree(ott_id(synons)) #checking which species are being left off tree
# in_tree #tells me which names are not in the tree
```
