---
title: "Main text figures: Objectives one and two"
author: "Erin Macartney, Szymek Drobniak, Shinichi Nakagawa, Malgorzata Lagisz"
output:
    rmdformats::readthedown:
      code_folding: hide
      code_download: true
      toc_depth: 4
editor_options:
  chunk_output_type: console
---

    
```{r, include = FALSE}
knitr::opts_chunk$set(
message = FALSE,
warning = FALSE,
cache = TRUE, 
tidy = TRUE, 
echo = TRUE
)

rm(list = ls())
```

### Seutup and data organisation

```{r setup, results = 'hide'}

knitr::opts_chunk$set(echo = TRUE)

library(readxl)
library(plyr)
library(here)
library(tibble)
library(dplyr)
library(tidyverse)
library(stringr)
library(knitr)
library(forcats)
library(ggplot2)
library(hrbrthemes) #for ggplot2
library(bibliometrix)
library(igraph)
library(patchwork)
library(RColorBrewer)
library(wordcloud2)
library(migest)
library(circlize)
```

``` {r, results = 'hide'}
#manually extracted data
xldata <- "./Data_extraction_postcrosschecking.xlsx"

# xldata <- read_excel(here("Data_extraction_postcrosschecking.xlsx"))
#note that here packeage doen't work with data wrangling code below

# #bibliometric data
# bib <- convert2df("./bibliometric.bib", dbsource = "scopus", format = "bibtex")

bib <- convert2df(here("bibliometric.bib"), dbsource = "scopus", format = "bibtex")
```

``` {r, results = 'hide'}
#Splitting list of tabs into separate dataframes
excel_sheets(path = xldata)
tab_names <- excel_sheets(path = xldata)


#creating a list of dataframes per tab
list_all <- lapply(tab_names, function(x) read_excel(path = xldata, sheet = x))

#assigning tab names to each dataframe
names(list_all) <- tab_names

#get dataframes out of list
list2env(list_all, .GlobalEnv)
```
# Objective One - Between discipline patterns 

## Figure 3 - Broad patterns {.tabset}

### Fig 3A - Time trend

``` {r}

Publication_info_discipline <- merge(Publication_info, Review_info)

Fig3a <- Publication_info_discipline %>% 
  count(year) %>%
  ggplot(aes(x = year, y = n)) +
  geom_col(aes(), width = 0.7) +
  xlim(2009, 2021.5) +
  ylim(0, 14.5) +
  geom_text(aes(label = n),vjust = -0.2) +
  theme_classic() +
  labs(x = "Year", y = "Article count")+
  theme(legend.position = "none", axis.title.x = element_text(size = 10))



Fig3a

```

### Fig. 3B - Disciplines

``` {r, results = 'hide'}

count_discipline <-Review_info %>% count(discipline_code) %>% arrange(desc(n)) 
percent_discipline <- count_discipline %>% mutate(percent = (n/sum(n))*100)
percent_discipline$percent <- round(percent_discipline$percent, digits = 0)
percent_discipline$discipline_code <- factor(percent_discipline$discipline_code, level = percent_discipline$discipline_code[order(percent_discipline$n, decreasing = TRUE)])

# brewer.pal(6, "Accent") # matching colours of disciplines from brewer used in other figs
# my.cols <- (c("#BEAED4","#FFFF99" ,"#386CB0","#7FC97F","#FDC086","#F0027F"))

Fig3b <- ggplot(percent_discipline, aes(x = discipline_code, y = percent)) + 
  geom_col(aes(), width = 0.7) + 
  geom_text(aes(label = percent), vjust = -0.2) +
  scale_y_continuous(name = "Percent (%)") +
  xlab("Discipline") + 
  # scale_fill_manual(values=my.cols) +
  theme_classic() 

Fig3b

#TODO may change colour scheme

```

### Fig. 3C - Species
Losia to do

### Fig. 3 - Panel

``` {r}
Fig3 <- Fig3a / Fig3b + plot_annotation(tag_levels = "A")

Fig3 
```

## Figure 4 - Research patterns {.tabset}

### Fig. 4A - Inter- vs trans- inheritance


``` {r}

count_inter_vs_trans <- count(Inter_vs_trans_info, inter_vs_trans_code)
percent_inter_vs_trans <- count_inter_vs_trans %>% mutate(percent = (n/sum(n))*100)

percent_inter_vs_trans$percent <- round(percent_inter_vs_trans$percent, digits = 0)

Fig4a <- ggplot(percent_inter_vs_trans, aes(x = inter_vs_trans_code, y = percent)) +
  geom_col(aes(), width = 0.7) +
  coord_flip() + 
  labs(y = "Percent (%)") +
  ylim(0,100)+
  geom_text(aes(label = percent), hjust = -0.2) +
  theme_classic() +
  labs(x = "Inter- vs trans-inheritnace")

Fig4a
```

### Fig. 4B - Transmission mode 

```{r}

count_transmission <- count(Transmission_info, transmission_code)
percent_transmission <- count_transmission %>% mutate(percent = (n/sum(n))*100)

percent_transmission$percent <- round(percent_transmission$percent, digits = 0)

Fig4b <- ggplot(percent_transmission, aes(x = reorder(transmission_code, -percent), y = percent)) + 
  geom_col(aes(), width = 0.7) +
  coord_flip() + 
  labs(y = "Percent (%)") +
  ylim(0,100) +
  geom_text(aes(label = percent), hjust = -0.2)+
  theme_classic() +
  labs(x = "Transmission mode")

Fig4b

```

### Fig. 4C - Terminology match vs mismatch
```{r}

count_terminology <- count(Review_info, terminology_code)
percent_terminology <- count_terminology %>% mutate(percent = (n/sum(n))*100)

percent_terminology$percent <- round(percent_terminology$percent, digits = 0)

Fig4c <- ggplot(percent_terminology, aes(x =reorder(terminology_code, -percent), y = percent)) + 
  coord_flip() + 
  geom_col(aes(), width = 0.7) + 
  labs(y = "Percent (%)",x = "Terminology use matches Fig. 1" ) +
  ylim(0,100) +
  geom_text(aes(label = percent), hjust = -0.2)+
  theme_classic()


Fig4c

```

### Fig. 4D - Type of F0 exposure

```{r}

count_F0_env <- count(F0_env_info, F0_env_code)
percent_F0_env <- count_F0_env %>% mutate(percent = (n/sum(n))*100)

percent_F0_env$percent <- round(percent_F0_env$percent, digits = 0)

Fig4d <- ggplot(percent_F0_env, aes(x = reorder(F0_env_code, -percent), y = percent)) + 
  geom_col(aes(), width = 0.7) +
  coord_flip() + 
  labs(y = "Percent (%)",x = "Type of environmental exposure" ) +
  ylim(0,100) +
  geom_text(aes(label = percent), hjust = -0.2)+
  theme_classic()
  
Fig4d
```

### Fig. 4E - Timing of F0 exposure

```{r}

count_exposure_timing <- count(Exposure_timing_info, exposure_timing_code)
percent_exposure_timing <- count_exposure_timing %>% mutate(percent = (n/sum(n))*100)

percent_exposure_timing$percent <- round(percent_exposure_timing$percent, digits = 0)

Fig4e<- ggplot(percent_exposure_timing, aes(x = reorder(exposure_timing_code, -percent), y = percent)) + 
  geom_col(aes(), width = 0.7) + 
   coord_flip() + 
  labs(y = "Percent (%)",x = "Timing of F0 (ancestor) exposure" ) +
  ylim(0,100) +
  geom_text(aes(label = percent), hjust = -0.2)+
  theme_classic()

Fig4e
```

### Fig. 4F - Descendant trait

```{r}
count_descendant_trait <- count(Descendant_trait_info, descendant_trait_code)
percent_descendant_trait <- count_descendant_trait%>% mutate(percent = (n/sum(n))*100)
percent_descendant_trait$percent <- round(percent_descendant_trait$percent, digits = 0)


Fig4f<- ggplot(percent_descendant_trait, aes(x = reorder(descendant_trait_code, -percent), y = percent)) + 
  geom_col(aes(), width = 0.7) + 
  coord_flip() + 
  labs(y = "Percent (%)",x = "Descendant traits" ) +
  ylim(0,100) +
  geom_text(aes(label = percent), hjust = -0.2)+
  theme_classic()

Fig4f
```

### Fig. 4G - Descendant sex

```{r}

count_descendant_sex <- count(Descendant_sex_info, descendant_sex_code)
percent_descendant_sex <- count_descendant_sex%>% mutate(percent = (n/sum(n))*100)
percent_descendant_sex$percent <- round(percent_descendant_sex$percent, digits = 0)


Fig4g <- ggplot(percent_descendant_sex, aes(x = reorder(descendant_sex_code, -percent), y = percent)) + 
  geom_col(aes(), width = 0.7) + 
  coord_flip() + 
  labs(y = "Percent (%)",x = "Descendant sex" ) +
  ylim(0,100) +
  geom_text(aes(label = percent), hjust = -0.2)+
  theme_classic()

Fig4g

```

### Fig. 4H - Environmental effect direction 

```{r}

count_env_eff <- count(Env_eff_diection_info, env_eff_direction_code)
percent_env_eff <- count_env_eff%>% mutate(percent = (n/sum(n))*100)
percent_env_eff$percent <- round(percent_env_eff$percent, digits = 0)


Fig4h <- ggplot(percent_env_eff, aes(x = reorder(env_eff_direction_code, -percent), y = percent)) + 
  geom_col(aes(), width = 0.7) + 
  coord_flip() +
  labs(y = "Percent (%)",x = "Environmental effect direction" ) +
  ylim(0,100) +
  geom_text(aes(label = percent), hjust = -0.2)+
  theme_classic()
  
Fig4h

```

### Fig. 4 - Panel 

```{r}
Fig4 <- ((Fig4a | Fig4b | Fig4c | Fig4d) / (Fig4e | Fig4f | Fig4f | Fig4h)) + plot_annotation(tag_levels = "A")

Fig4

#TODO remove x axis label from a -d
```
