---
title: "Appendix S4"
author: "Erin Macartney, Szymek Drobniak, Shinichi Nakagawa, Malgorzata Lagisz"
date: "17/06/2022"
output:
    rmdformats::readthedown:
      code_folding: hide
      code_download: true
      toc_depth: 4
editor_options:
  chunk_output_type: console
---

    
```{r, include = FALSE}
knitr::opts_chunk$set(
message = FALSE,
warning = FALSE,
cache = TRUE,
tidy = TRUE,
echo = TRUE
)

rm(list = ls())
```

### Setup and data organisation

```{r setup, results = 'hide'}

knitr::opts_chunk$set(echo = TRUE)

pacman::p_load(readxl,
               plyr,
               here,
               tibble,
               dplyr,
               tidyverse,
               stringr,
               knitr,
               forcats,
               ggplot2,
               hrbrthemes,
               bibliometrix,
               patchwork,
               migest,
               circlize,
               rotl,
               ape,
               ggnewscale,
               ggtree,
               ggtreeExtra,
               igraph,
               stringi,
               tidystringdist,
               stringdist,
               fuzzyjoin,
               # ggthemes,
               viridis,
               cowplot,
               mapproj,
               wordcloud2)

#install ggtreeExtra
# if (!require("BiocManager", quietly = TRUE))
#     install.packages("BiocManager")
# BiocManager::install("ggtreeExtra")

```

``` {r load files, results = 'hide'}

#manually extracted data
xldata <- "./Data/Data_extraction_postcrosschecking.xlsx"

bib <- convert2df(here("data","bibliometric2.bib"), dbsource = "scopus", format = "bibtex")

```

``` {r slitting sheets, results = 'hide'}
#Splitting list of tabs into separate dataframes
excel_sheets(path = xldata)
tab_names <- excel_sheets(path = xldata)

#creating a list of dataframes per tab
list_all <- lapply(tab_names, function(x) read_excel(path = xldata, sheet = x))

#assigning tab names to each dataframe
names(list_all) <- tab_names

#get dataframes out of list
list2env(list_all, .GlobalEnv)
```

# Fig. S2 - Filial generations within and between disciplines

```{r}
merged_descendant_generat <- merge(Descendant_generat_info, Review_info)

count_descendant_generat <- merged_descendant_generat %>% count(descendant_generat_code, by = discipline_code) %>% arrange(desc(n))
percent_descendant_generat <- count_descendant_generat %>% mutate(percent = (n/sum(n))*100)

percent_descendant_generat <- percent_descendant_generat %>%
  rename (
    discipline_code = by
  )


percent_descendant_generat <- subset(percent_descendant_generat, descendant_generat_code != "NA")

my.cols <- (c("#66C2A5", "#FC8D62", "#8DA0CB", "#E78AC3", "#A6D854", "#FFD92F"))

percent_descendant_generat$descendant_generat_code <- factor(percent_descendant_generat$descendant_generat_code ,levels = c("F1", "F2", "F3", "F4", "F5", "F6", "F200"))

FigS2 <- ggplot(percent_descendant_generat, aes(x = descendant_generat_code, y = percent)) +
  geom_col(aes(fill = discipline_code), width = 0.7) +
  theme_light() +
  coord_flip() +
  scale_y_continuous(name = "Percent (%)") +
  theme(legend.position = "bottom", axis.title.x = element_text(size = 10), axis.title.y = element_blank()) +
  guides(fill=guide_legend(title="Discipline")) + 
  scale_fill_manual(values=my.cols)

FigS2

```

**Fig. S2** Bar chart showing percent of SRs within and between generations that included primary studies of ancestral environmental effects on descendant filial generations.

# Fig. S3 - Word cloud across disciplines


``` {r, message = FALSE, warning = FALSE, results = 'hide'}
bib2 <- biblioAnalysis(bib, sep = ";")
S <- summary(object = bib2, k = 50, pause = FALSE)
```

``` {r, message = FALSE, warning = FALSE}
keywords <- S$MostRelKeywords
words<-keywords[,1]
freq<-as.numeric(keywords[,2])
prob<-freq/sum(freq)

FigS3 <- wordcloud2(data.frame(words, prob), shuffle = TRUE, size = 0.5, color = 'random-dark')

FigS3
```

**Fig. S3** Word cloud of the most common key words across disciplines

# Fig. S5 - CEESAT individual scores

```{r}
#blinding authors
Assessment$id <- paste("ID", c(1:length(Assessment$id)), sep = "")
#shortening column names
names(Assessment) <- gsub("CEESAT_", "", names(Assessment), fixed = TRUE)
#selecting only the columns with scores
#selecting only the columns with scores
Assessment_reduced <- select(Assessment, c("id", !ends_with("_comment")))
#wrangling data into long format
ceesat_long <- gather(Assessment_reduced, question, score, Q1.1:Q8.1, factor_key=TRUE)
```

``` {r}

FigS4 <- ggplot(data = ceesat_long, aes(y = id, x = question)) +
  geom_tile(color="black", fill="white", size = 0.5) +
  geom_point(aes(color = as.factor(score)), size = 3) +
  scale_x_discrete(position = "top") +
  guides(color = guide_legend(reverse = TRUE)) +
  scale_color_manual(values = c("orange","yellow","green","red" ), name = "Score:") + 
  theme_minimal() + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        legend.position = "none",
        legend.text = element_text(size = 12),
        axis.text.y = element_text(size = 5, color = "black"),
        axis.text.x = element_text(angle = 45, hjust=0)
  ) +
  ylab("Study ID") + 
  xlab("CEESAT question") 

FigS4
```

**Fig. S4** Individual CEESAT scores across SRs. Red = red score, orange = amber score, green = green score, yellow= gold score. See Appendix S2 for individual questions and requisites for each score. 