---
title: "Main Figures"
author: "Erin Macartney, Szymek Drobniak, Shinichi Nakagawa, Malgorzata Lagisz"
output:
    rmdformats::readthedown:
      code_folding: hide
      code_download: true
      toc_depth: 4
editor_options:
  chunk_output_type: console
---

    
```{r, include = FALSE}
knitr::opts_chunk$set(
message = FALSE,
warning = FALSE,
cache = TRUE,
tidy = TRUE,
echo = TRUE
)

rm(list = ls())
```

### Setup and data organisation

```{r setup, results = 'hide'}

knitr::opts_chunk$set(echo = TRUE)

pacman::p_load(readxl,
               plyr,
               here,
               tibble,
               dplyr,
               tidyverse,
               stringr,
               knitr,
               forcats,
               ggplot2,
               hrbrthemes,
               bibliometrix,
               patchwork,
               migest,
               circlize,
               rotl,
               ape,
               ggnewscale,
               ggtree,
               ggtreeExtra,
               igraph,
               stringi,
               tidystringdist,
               stringdist,
               fuzzyjoin,
               # ggthemes,
               viridis,
               cowplot,
               mapproj)

#install ggtreeExtra
if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install("ggtreeExtra")
               
# library(wordcloud2)

```

``` {r load files, results = 'hide'}

#manually extracted data
xldata <- "./Data/Data_extraction_postcrosschecking.xlsx"
#note that using here function does work for datawrangling below

bib <- convert2df(here("Data","bibliometric2.bib"), dbsource = "scopus", format = "bibtex")

```

``` {r slitting sheets, results = 'hide'}
#Splitting list of tabs into separate dataframes
excel_sheets(path = xldata)
tab_names <- excel_sheets(path = xldata)

#creating a list of dataframes per tab
list_all <- lapply(tab_names, function(x) read_excel(path = xldata, sheet = x))

#assigning tab names to each dataframe
names(list_all) <- tab_names

#get dataframes out of list
list2env(list_all, .GlobalEnv)
```

# Objective One - Across discipline patterns 

## Figure 3  - Time trend

``` {r fig3}

Publication_info_discipline <- merge(Publication_info, Review_info)

Fig3 <- Publication_info_discipline %>% 
  count(year) %>%
  ggplot(aes(x = year, y = n)) +
  geom_col(aes(), width = 0.7) +
  xlim(2009, 2021.5) +
  ylim(0, 14.5) +
  geom_text(aes(label = n),vjust = -0.2) +
  theme_classic() +
  labs(x = "Year", y = "Article count")+
  theme(legend.position = "none", axis.title.x = element_text(size = 10))

Fig3

#exported PDF as 5x7 inch
```

## Figure 4  - Species tree

``` {r fig4, results = 'hide', echo = FALSE}
#Making the tree

# length(unique(Species_info$species_name)) #354
# unique(Species_info$species_name) #needs cleaning
#get rid of the underscores
Species_info$species_name <- gsub("_"," ", Species_info$species_name)
# Make a table of how many words each name has:
table((lengths(gregexpr("\\W+", Species_info$species_name)) + 1)) #20 records with >2 words species names (subspecies etc.)
 
#taxa <- tnrs_match_names(unique(Species_info$species_name)) #fails due to non-recognizable names

# Fix obviously incompatible names (subspecies, name variants):
Species_info$species_name[Species_info$species_name == "Pinus elliottii Engelm"] <- "Pinus elliottii"
Species_info$species_name[Species_info$species_name == "Chlamydotis undulata undulata"] <- "Chlamydotis undulata"
Species_info$species_name[Species_info$species_name == "Apis mellifera capensis"] <- "Apis mellifera"
Species_info$species_name[Species_info$species_name == "Capra aegagrus hircus"] <- "Capra hircus"
Species_info$species_name[Species_info$species_name == "Sus scrofa domesticus"] <- "Sus scrofa"
Species_info$species_name[Species_info$species_name == "Sus domesticus"] <- "Sus scrofa"
Species_info$species_name[Species_info$species_name == "Equus ferus caballus"] <- "Equus ferus"
Species_info$species_name[Species_info$species_name == "Coturnix coturnix japonica"] <- "Coturnix japonica"
Species_info$species_name[Species_info$species_name == "Chlorocebus aethiops sabaeus"] <- "Chlorocebus sabaeus"
Species_info$species_name[Species_info$species_name == "Gallus gallus domesticus"] <- "Gallus gallus"
Species_info$species_name[Species_info$species_name == "Parus caeruleus"] <- "Cyanistes caeruleus"
Species_info$species_name[Species_info$species_name == "Poecilopsis gracilis"] <- "Poeciliopsis catemaco"
Species_info$species_name[Species_info$species_name == "Campanulastrum americanum"] <- "Campanula americana"
Species_info$species_name[Species_info$species_name == "Carpodacus mexicanus"] <- "Haemorhous mexicanus"
Species_info$species_name[Species_info$species_name == "Caryedon palaestinicus"] <- "Caryedon serratus"
Species_info$species_name[Species_info$species_name == "Galinsoga ciliata"] <- "Galinsoga quadriradiata"
Species_info$species_name[Species_info$species_name == "Hydroides diramphus"] <- "Hydroides dirampha"
Species_info$species_name[Species_info$species_name == "Lymantria dispa"] <- "Lymantria dispar"
Species_info$species_name[Species_info$species_name == "Mimulus guttatus"] <- "Erythranthe guttata"
Species_info$species_name[Species_info$species_name == "Lymantria dispa"] <- "Lymantria dispar"
Species_info$species_name[Species_info$species_name == "Oryza indica"] <- "Oryza sativa"
Species_info$species_name[Species_info$species_name == "Physella acuta"] <- "Physa acuta"
Species_info$species_name[Species_info$species_name == "Pinus caribaea"] <- "Pinus cubensis" #reverse later
Species_info$species_name[Species_info$species_name == "Racesina luteola"] <- "Cerasina luteola" #reverse later
Species_info$species_name[Species_info$species_name == "Chrysanthemum nankingense"] <- "Chrysanthemum boreale" #reverse later
Species_info$species_name[Species_info$species_name == "Cyprinodon variegatus"] <- "Cyprinodon" #reverse later

Species_info$species_name[Species_info$species_name == "Mus domesticus"] <- "Mus musculus"

Species_info <- Species_info[Species_info$species_name != "NA", ]

table(Species_info$species_name, useNA = "always") #no NA
length(unique(Species_info$species_name)) #344

taxa <- tnrs_match_names(unique(Species_info$species_name))
table(taxa$approximate_match) ##11 approximate matches
table(taxa$flags) # flags 8 names with problems (hidden, hybrid, incertae_sedis_inherited, infraspecific, infraspecific) - will need fixing

# mytree <- tol_induced_subtree(ott_ids = taxa$ott_id, label_format= "name") #this will fail with: Error: HTTP failure: 400
#[/v3/tree_of_life/induced_subtree] Error: node_id 'ott768010' was not found!list(ott1014334 = "pruned_ott_id", ott3899190 = "pruned_ott_id", ott3904118 = "pruned_ott_id", ott4279984 = "pruned_ott_id", ott5147008 = "pruned_ott_id", ott768010 = "pruned_ott_id")
 
taxa[taxa[["ott_id"]] == "768010", ] #Peringia ulvae - "unplaced_inherited"
Species_info$species_name[Species_info$species_name == "Peringia ulvae"] <- "Peringia"
Species_info$species_name[Species_info$species_name == "Peringia"] <- "Hydrobia acuta"
taxa[taxa[["ott_id"]] == "1014334", ] #Euoniticellus intermedius - "incertae_sedis_inherited"
Species_info$species_name[Species_info$species_name == "Euoniticellus intermedius"] <- "Euoniticellus"
taxa[taxa[["ott_id"]] == "328990", ] # Euoniticellus - still "incertae_sedis", replace with "Anoplodrepanus""
Species_info$species_name[Species_info$species_name == "Euoniticellus"] <- "Anoplodrepanus reconditus"

taxa[taxa[["ott_id"]] == "3899190", ] #Chrysanthemum x morifolium - "hybrid"
Species_info$species_name[Species_info$species_name == "Chrysanthemum morifolium"] <- "Chrysanthemum indicum"

taxa[taxa[["ott_id"]] == "3904118", ] #Fragaria x ananassa - "hybrid" (Fragaria chiloensis x Fragaria virginiana) 
Species_info$species_name[Species_info$species_name == "Fragaria ananassa"] <- "Fragaria chiloensis"

taxa[taxa[["ott_id"]] == "4279984", ] #Poecilopsis gracilis - "hidden, sibling_higher"
#"Poecilopsis gracilis" -> Poecilopsis (genus-rank name) fix:
Species_info$species_name[Species_info$species_name == "Poecilopsis gracilis"] <- "Poecilopsis catemaco"

taxa[taxa[["ott_id"]] == "5147008", ] #Populus x beijingensis  - "hybrid": P. beijingensis (P. nigra var. italica × P. cathayana)
Species_info$species_name[Species_info$species_name == "Populus beijingensis"] <- "Populus cathayana"

#"Ludwigia hexapetala" gets recognised as a subspecies Ludwigia_grandiflora_subsp._hexapetala
Species_info$species_name[Species_info$species_name == "Ludwigia hexapetala"] <- "Ludwigia grandiflora"

## re-run raxa matching and tree retrieval:
taxa <- tnrs_match_names(unique(Species_info$species_name)) #runs fine
table(taxa$approximate_match) #12 approximate matches
table(taxa$flags) # flags 2 names with problems (incertae_sedis_inherited) - will need fixing
mytree <- tol_induced_subtree(ott_ids = taxa$ott_id, label_format= "name") #this now works fine

## Tree tip labels need some cleaning:
mytree$tip.label <- gsub("\\(.*", "", mytree$tip.label) #remove comments
mytree$tip.label <- gsub("_"," ", mytree$tip.label) #get rid of the underscores
mytree$tip.label <- trimws(mytree$tip.label) #getting rid of the trailing whitespace

## Reverse substitutions of species names in the tree tip labels:
mytree$tip.label[mytree$tip.label == "Hydrobia acuta"] <- "Peringia ulvae"
mytree$tip.label[mytree$tip.label == "Anoplodrepanus reconditus"] <- "Euoniticellus intermedius"
mytree$tip.label[mytree$tip.label == "Chrysanthemum indicum"] <- "Chrysanthemum morifolium"
mytree$tip.label[mytree$tip.label == "Fragaria chiloensis"] <- "Fragaria ananassa" 
mytree$tip.label[mytree$tip.label == "Poecilopsis catemaco"] <- "Poecilopsis gracilis"
mytree$tip.label[mytree$tip.label == "Populus cathayana"] <- "Populus beijingensis"
mytree$tip.label[mytree$tip.label == "Ludwigia grandiflora"] <- "Ludwigia hexapetala"
mytree$tip.label[mytree$tip.label == "Pinus cubensis"] <- "Pinus caribaea" 
mytree$tip.label[mytree$tip.label == "Cerasina luteola"] <- "Racesina luteola"
mytree$tip.label[mytree$tip.label == "Chrysanthemum boreale"] <- "Chrysanthemum nankingense"
mytree$tip.label[mytree$tip.label == "Cyprinodon"] <- "Cyprinodon variegatus"

## Other substitutions of species names made in the tree tip labels:
mytree$tip.label[mytree$tip.label == "Taraxacum adiantifrons"] <- "Taraxacum hemicyclum"
mytree$tip.label[mytree$tip.label == "Trichogramma bezdencovii"] <- "Trichogramma telengai"
mytree$tip.label[mytree$tip.label == "Pan"] <- "Pan troglodytes"
mytree$tip.label[mytree$tip.label == "Vulpes lagopus"] <- "Alopex lagopus"
mytree$tip.label[mytree$tip.label == "Pelophylax lessonae"] <- "Rana lessonae"
mytree$tip.label[mytree$tip.label == "Diodella teres"] <- "Diodia teres" 
mytree$tip.label[mytree$tip.label == "Solidago canadensis"] <- "Solidago altissima"
mytree$tip.label[mytree$tip.label == "Radix balthica"] <- "Ampullaceana balthica"
mytree$tip.label[mytree$tip.label == "Magallana gigas"] <- "Crassostrea gigas"
mytree$tip.label[mytree$tip.label == "Derocephalus angusticollis"] <- "Telostylinus angusticollis" 
mytree$tip.label[mytree$tip.label == "Carinascincus metallicus"] <- "Niveoscincus metallicus" 
mytree$tip.label[mytree$tip.label == "Pecari tajacu"] <- "Dicotyles tajacu" 
mytree$tip.label[mytree$tip.label == "Palaemon pugio"] <- "Palaemonetes pugio" 

## Reverse substitutions of species names in the species list:
Species_info$species_name[Species_info$species_name == "Hydrobia acuta"] <- "Peringia ulvae"
Species_info$species_name[Species_info$species_name == "Anoplodrepanus reconditus"] <- "Euoniticellus intermedius"
Species_info$species_name[Species_info$species_name == "Chrysanthemum indicum"] <- "Chrysanthemum morifolium"
Species_info$species_name[Species_info$species_name == "Fragaria chiloensis"] <- "Fragaria ananassa" 
Species_info$species_name[Species_info$species_name == "Poecilopsis catemaco"] <- "Poecilopsis gracilis"
Species_info$species_name[Species_info$species_name == "Populus cathayana"] <- "Populus beijingensis"
Species_info$species_name[Species_info$species_name == "Ludwigia grandiflora"] <- "Ludwigia hexapetala"
Species_info$species_name[Species_info$species_name == "Pinus cubensis"] <- "Pinus caribaea" 
Species_info$species_name[Species_info$species_name == "Cerasina luteola"] <- "Racesina luteola" 
Species_info$species_name[Species_info$species_name == "Chrysanthemum boreale"] <- "Chrysanthemum nankingense" 
Species_info$species_name[Species_info$species_name == "Cyprinodon"] <- "Cyprinodon variegatus"

#Fix more names in the species list:
Species_info$species_name[Species_info$species_name == "Strongylocentrotus franciscanus"] <- "Mesocentrotus franciscanus"
Species_info$species_name[Species_info$species_name == "Mytilus chilensis"] <- "Mytilus edulis"
Species_info$species_name[Species_info$species_name == "Populus pseudo-simonii"] <- "Populus pseudosimonii"
Species_info$species_name[Species_info$species_name == "Bythotrephes longima"] <- "Bythotrephes longimanus"
Species_info$species_name[Species_info$species_name == "Biomphalaria galbrata"] <- "Biomphalaria glabrata"
Species_info$species_name[Species_info$species_name == "Niveoscincus ocellatus"] <- "Carinascincus ocellatus"
Species_info$species_name[Species_info$species_name == "Polygonum dropiper"] <- "Persicaria hydropiper"
Species_info$species_name[Species_info$species_name == "Polygonum persicaria"] <- "Persicaria glabra"
Species_info$species_name[Species_info$species_name == "Priapichthys festae"] <- "Pseudopoecilia festae"

sort(intersect(as.character(mytree$tip.label), unique(Species_info$species_name))) ## 335 names are matching - all fixed 
sort(setdiff(unique(Species_info$species_name), as.character(mytree$tip.label))) ## names not matching - not in tip.label
sort(setdiff(as.character(mytree$tip.label), unique(Species_info$species_name))) ## names not matching - not in species_name

# plot(mytree, show.tip.label = T, cex = 0.8, no.margin = TRUE)
# str(mytree) #335 tips

# write.tree(mytree, file = "species_tree.tre") #save the tree 
# 
# write.csv(Species_info, file = "Species_info.csv")
```

```{r plot tree}

sample_data <- count(Species_info, species_name)
sample_data <- as.data.frame(sample_data)
sample_data2 <-mutate(sample_data, tip.label = species_name)
mytree$tip.label <- strip_ott_ids(mytree$tip.label, remove_underscores = TRUE)
# summary(sample_data2$tip.label)
# sample_data2$count <- as.numeric(sample_data2$count)
sample_data3 <- left_join(sample_data2, Species_info[,c("species_name","broad_taxa")], by = "species_name")
sample_data4 <- distinct(sample_data3, species_name, .keep_all = TRUE)
# is.na(sample_data4)
sample_data4$species_name<- as.factor(sample_data4$species_name)
sample_data4$tip.label <- as.factor(sample_data4$tip.label)
sample_data4$broad_taxa<- as.factor(sample_data4$broad_taxa)

# count_taxa <- count(sample_data4, broad_taxa)
# percent_taxa <- count_taxa%>% mutate(percent = (n/sum(n))*100)

cols <- c("yellow", "violet", "turquoise", "tomato", "thistle", "springgreen", "navy", "orange", "lightgoldenrod", "lightpink", "khaki", "lightslateblue", "red", "magenta3", "plum", "hotpink4","seagreen", "olivedrab")

tree2 <- ggtree(mytree, layout = "circular", lwd = 0.75) %<+% sample_data4 + aes(col = broad_taxa)+ theme(legend.position = "bottom") + scale_colour_manual(values = cols, (title = "Broad taxa"))

tree3 <- tree2 + new_scale_fill() + geom_fruit(geom = geom_bar, mapping = aes(x = log10(n), col = "gray30"), stat = "identity", col = "gray30", orientation = "y", axis.params = list(axis = "x",text.angle = -45, hjust = 0, text.size = 3), grid.params = list(alpha = 0.35),offset = 0.085, pwidth = 0.55, alpha = 0.8) + guides(fill ="none")

tree3

# count(sample_data4, broad_taxa)
# count(sample_data4, species_name)

## will add silhouettes to most common species manually
```

## Figure 5 - Between discipline patterns {.tabset}

### Fig. 5A - Inter- vs trans- inheritance

``` {r fig5a}
count_inter_vs_trans <- count(Inter_vs_trans_info, inter_vs_trans_code)
percent_inter_vs_trans <- count_inter_vs_trans %>% mutate(percent = (n/sum(n))*100)

percent_inter_vs_trans$percent <- round(percent_inter_vs_trans$percent, digits = 0)

Fig5a <- ggplot(percent_inter_vs_trans, aes(x = inter_vs_trans_code, y = percent)) +
  geom_col(aes(), width = 0.7) +
  coord_flip() + 
  labs(y = "Percent (%)") +
  ylim(0,100)+
  geom_text(aes(label = percent), hjust = -0.2) +
  theme_classic() +
  labs(x = "Inter- vs trans-inheritnace")

Fig5a
```

### Fig. 5B - Terminology match vs mismatch

```{r fig5b}

count_terminology <- count(Review_info, terminology_code)
percent_terminology <- count_terminology %>% mutate(percent = (n/sum(n))*100)

percent_terminology$percent <- round(percent_terminology$percent, digits = 0)

Fig5b <- ggplot(percent_terminology, aes(x =reorder(terminology_code, -percent), y = percent)) + 
  coord_flip() + 
  geom_col(aes(), width = 0.7) + 
  labs(y = "Percent (%)",x = "Terminology use matches \n Fig. 1") +
  ylim(0,100) +
  geom_text(aes(label = percent), hjust = -0.2)+
  theme_classic()
  

Fig5b

```

### Fig. 5C - Type of F0 exposure

```{r fig5c}

count_F0_env <- count(F0_env_info, F0_env_code)
percent_F0_env <- count_F0_env %>% mutate(percent = (n/sum(n))*100)

percent_F0_env$percent <- round(percent_F0_env$percent, digits = 0)

Fig5c <- ggplot(percent_F0_env, aes(x = reorder(F0_env_code, -percent), y = percent)) + 
  geom_col(aes(), width = 0.7) +
  coord_flip() + 
  labs(y = "Percent (%)",x = "Type of environmental \n exposure" ) +
  ylim(0,100) +
  geom_text(aes(label = percent), hjust = -0.2)+
  theme_classic()
  
Fig5c
```

### Fig. 5D - Transmission mode 

```{r fig5d}

count_transmission <- count(Transmission_info, transmission_code)
percent_transmission <- count_transmission %>% mutate(percent = (n/sum(n))*100)

percent_transmission$percent <- round(percent_transmission$percent, digits = 0)

Fig5d <- ggplot(percent_transmission, aes(x = reorder(transmission_code, -percent), y = percent)) + 
  geom_col(aes(), width = 0.7) +
  coord_flip() + 
  labs(y = "Percent (%)") +
  ylim(0,100) +
  geom_text(aes(label = percent), hjust = -0.2)+
  theme_classic() +
  labs(x = "Transmission mode")

Fig5d

```

### Fig. 5E - Timing of F0 exposure

```{r fig5e}

count_exposure_timing <- count(Exposure_timing_info, exposure_timing_code)
percent_exposure_timing <- count_exposure_timing %>% mutate(percent = (n/sum(n))*100)

percent_exposure_timing$percent <- round(percent_exposure_timing$percent, digits = 0)

Fig5e<- ggplot(percent_exposure_timing, aes(x = reorder(exposure_timing_code, -percent), y = percent)) + 
  geom_col(aes(), width = 0.7) + 
   coord_flip() + 
  labs(y = "Percent (%)",x = "Timing of F0 (ancestor) \n exposure" ) +
  ylim(0,100) +
  geom_text(aes(label = percent), hjust = -0.2)+
  theme_classic()

Fig5e
```

### Fig. 5F - Descendant trait

```{r fig5f}
count_descendant_trait <- count(Descendant_trait_info, descendant_trait_code)
percent_descendant_trait <- count_descendant_trait%>% mutate(percent = (n/sum(n))*100)
percent_descendant_trait$percent <- round(percent_descendant_trait$percent, digits = 0)


Fig5f<- ggplot(percent_descendant_trait, aes(x = reorder(descendant_trait_code, -percent), y = percent)) + 
  geom_col(aes(), width = 0.7) + 
  coord_flip() + 
  labs(y = "Percent (%)",x = "Descendant traits" ) +
  ylim(0,100) +
  geom_text(aes(label = percent), hjust = -0.2)+
  theme_classic()

Fig5f
```

### Fig. 5G - Descendant sex

```{r fig5g}

count_descendant_sex <- count(Descendant_sex_info, descendant_sex_code)
percent_descendant_sex <- count_descendant_sex%>% mutate(percent = (n/sum(n))*100)
percent_descendant_sex$percent <- round(percent_descendant_sex$percent, digits = 0)


Fig5g <- ggplot(percent_descendant_sex, aes(x = reorder(descendant_sex_code, -percent), y = percent)) + 
  geom_col(aes(), width = 0.7) + 
  coord_flip() + 
  labs(y = "Percent (%)",x = "Descendant sex" ) +
  ylim(0,100) +
  geom_text(aes(label = percent), hjust = -0.2)+
  theme_classic()

Fig5g

```

### Fig. 5H - Environmental effect direction 

```{r fig5h}

count_env_eff <- count(Env_eff_diection_info, env_eff_direction_code)
percent_env_eff <- count_env_eff%>% mutate(percent = (n/sum(n))*100)
percent_env_eff$percent <- round(percent_env_eff$percent, digits = 0)


Fig5h <- ggplot(percent_env_eff, aes(x = reorder(env_eff_direction_code, -percent), y = percent)) + 
  geom_col(aes(), width = 0.7) + 
  coord_flip() +
  labs(y = "Percent (%)",x = "Environmental effect \n direction" ) +
  ylim(0,100) +
  geom_text(aes(label = percent), hjust = -0.2)+
  theme_classic()
  
Fig5h

```

### Fig. 5 - Panel 

```{r fig5panel,  fig.width=15, fig.height=20}
Fig5 <- ((Fig5a | Fig5b) / (Fig5c | Fig5d) / (Fig5e | Fig5f) / (Fig5g | Fig5h)) + plot_annotation(tag_levels = "A")

Fig5

#exported as PDF 20x15 inch

```

# Objective Two

## Figure 6 - Disciplines and taxa {.tabset}

### Fig. 6A - Percent SRs within disciplines

``` {r fig6a, results = 'hide'}
Review_info$discipline_code<-as.factor(Review_info$discipline_code)

count_discipline <- Review_info %>% count(discipline_code)
percent_discipline <- count_discipline %>% mutate(percent = (n/sum(n))*100)
percent_discipline$percent <- round(percent_discipline$percent, digits = 0)

# brewer.pal(6, "Set2")
my.cols <- (c("#66C2A5", "#FC8D62", "#8DA0CB", "#E78AC3", "#A6D854", "#FFD92F"))

Fig6a <- ggplot(percent_discipline, aes(x = discipline_code, y = percent)) + 
  geom_col(aes(fill = discipline_code)) + 
  geom_text(aes(label = percent), vjust = -0.2) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(name = "Percent (%)") +
  xlab("Discipline") + 
  scale_fill_manual(values=my.cols) +
  theme_classic() +
  theme(legend.position = "none")

Fig6a

```

### Fig. 6B - Disciplines within taxa

``` {r fig6b}
Merged_taxa <- merge(Species_info, Review_info)
#creating a subset dataframe without repreated measures of taxa per species
Merged_taxa2 <- Merged_taxa[c("id", "broad_taxa", "discipline_code")]
Merged_taxa3 <- Merged_taxa2 %>% distinct(id, broad_taxa,.keep_all = TRUE)

count_taxa <- Merged_taxa3 %>% count(broad_taxa, by = discipline_code) %>% arrange(desc(n))


count_taxa <-count_taxa%>%
  rename(
    discipline_code = by
  )

count_taxa1 <- subset(count_taxa, broad_taxa != "unclear")

Fig6b <- ggplot(count_taxa1, aes(x = fct_rev(broad_taxa), y = n, fill = discipline_code)) +
  geom_bar(position = "fill", stat = "identity") + 
  theme_classic() +
  coord_flip() +
  labs(y = "Proportion", x = "Broad taxa", fill = "Discipline") +
  scale_fill_brewer(palette = "Set2") +
  theme(legend.position = "none")

Fig6b
```

### Fig. 6 - Panel

```{r fig6panel}
Fig6 <- (Fig6a + Fig6b) + plot_annotation(tag_levels = "A")

Fig6

#exported PDF as 5 x 10 inch

```

## Figure 7 - Between discipline research patterns {.tabset}

### Fig. 7A - Inter- vs trans- inheritance

``` {r fig7a}
Merged_inter_vs_trans <- merge(Inter_vs_trans_info, Review_info)

count_inter_vs_trans <- Merged_inter_vs_trans %>% count(inter_vs_trans_code, by = discipline_code ) %>% arrange(desc(n))

count_inter_vs_trans <-count_inter_vs_trans %>%
  rename(
    discipline_code = by
  )

Fig7a <- ggplot(count_inter_vs_trans, aes(y = discipline_code, x = inter_vs_trans_code, fill = n)) +
  geom_raster() + 
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Discipline", x = "Inter- vs trans-inheritance", fill = "Count") + 
  geom_text(aes(label = n)) + 
  scale_fill_gradient(low = "#FEE08B", high = "#D53E4F") +
  guides(fill = "none") 

Fig7a
```

### Fig. 7B - Terminology match vs mismatch

``` {r fig7b}
count_terminology <- Review_info %>% count(terminology_code, by = discipline_code) %>% arrange(desc(n))

count_terminology<- count_terminology %>%
  rename(
    discipline_code = by
  )

Fig7b <- ggplot(count_terminology, aes(x = reorder(terminology_code, -n), y = discipline_code, fill = n)) +
  geom_raster() + 
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Discipline", x = "Terminology use matches Fig. 1", fill = "Count") + 
  geom_text(aes(label = n)) + 
  scale_fill_gradient(low = "#FEE08B", high = "#D53E4F") +
  guides(fill = "none")

Fig7b

```

### Fig. 7C - Type of F0 exposure

```{r fig7c}

merged_F0_env <- merge(F0_env_info, Review_info)
count_F0_env<- merged_F0_env %>% count(F0_env_code, by = discipline_code ) %>% arrange(desc(n))
 
count_F0_env <-count_F0_env %>%
  rename(
    discipline_code = by
  )

Fig7c <- ggplot(count_F0_env, aes(y = discipline_code, x = F0_env_code, fill = n)) +
  geom_raster() + 
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Discipline", x = "Type of environmental exposure", fill = "Count") + 
  geom_text(aes(label = n)) + 
  scale_fill_gradient(low = "#FEE08B", high = "#D53E4F") +
  guides(fill = "none")

Fig7c
```

### Fig. 7D - Transmission mode

```{r fig7d}
Merged_transmission_info <- merge(Transmission_info, Review_info)

count_transmission <- Merged_transmission_info %>%  count(transmission_code, by = discipline_code) %>% arrange(desc(n))

count_transmission <-count_transmission %>%
  rename(
    discipline_code = by
  )

Fig7d <- ggplot(count_transmission, aes(y = discipline_code, x = transmission_code, fill = n)) +
  geom_raster() + 
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Discipline", x = "Transmission mode", fill = "Count") + 
  geom_text(aes(label = n)) + 
  scale_fill_gradient(low = "#FEE08B", high = "#D53E4F") +
  guides(fill = "none")

Fig7d

```

### Fig. 7E - Timing of F0 Exposure

```{r fig7e}

merged_exposure_timing <- merge(Exposure_timing_info, Review_info)

count_exposure_timing <- merged_exposure_timing %>% count(exposure_timing_code, by = discipline_code) %>% arrange(desc(n))

count_exposure_timing <- count_exposure_timing %>%
  rename (
    discipline_code = by
  )

Fig7e <- ggplot(count_exposure_timing, aes(y = discipline_code, x = exposure_timing_code, fill = n)) +
  geom_raster() + 
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Discipline", x = "Timing of F0 (ancestor) exposure", fill = "Count") + 
  geom_text(aes(label = n)) + 
  scale_fill_gradient(low = "#FEE08B", high = "#D53E4F") +
  guides(fill = "none")

Fig7e
```

### Fig. 7F - Descendant trait

```{r fig7f}

merged_descendant_trait <- merge(Descendant_trait_info, Review_info)
count_descendant_trait <- merged_descendant_trait %>% count(descendant_trait_code, by = discipline_code) %>% arrange(desc(n))

count_descendant_trait <- count_descendant_trait %>%
  rename(
    discipline_code = by
  )

Fig7f <- ggplot(count_descendant_trait, aes(y = discipline_code, x = descendant_trait_code, fill = n)) +
  geom_raster() + 
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Discipline", x = "Descendant traits", fill = "Count") + 
  geom_text(aes(label = n)) + 
  scale_fill_gradient(low = "#FEE08B", high = "#D53E4F") +
  guides(fill = "none")

Fig7f
```

### Fig. 7G - Descendant sex

```{r fig7g}

merged_descendant_sex <- merge(Descendant_sex_info, Review_info)
count_descendant_sex <- merged_descendant_sex %>% count(descendant_sex_code, by = discipline_code) %>% arrange(desc(n))

count_descendant_sex <- count_descendant_sex %>%
  rename(
    discipline_code = by
           )

Fig7g <- ggplot(count_descendant_sex, aes(y = discipline_code, x = descendant_sex_code, fill = n)) +
  geom_raster() + 
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Discipline", x = "Descendant sex", fill = "Count") + 
  geom_text(aes(label = n)) + 
  scale_fill_gradient(low = "#FEE08B", high = "#D53E4F") +
  guides(fill = "none")

Fig7g
```

### Fig. 7H - Environmental effect direction 

```{r fig7h}

merged_env_eff <- merge(Env_eff_diection_info, Review_info)

count_env_eff <- merged_env_eff %>% count(env_eff_direction_code, by = discipline_code) %>% arrange(desc(n))

count_env_eff <-count_env_eff %>%
  rename(
    discipline_code = by
  )

Fig7h <- ggplot(count_env_eff, aes(y = discipline_code, x = env_eff_direction_code, fill = n)) +
  geom_raster() + 
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Discipline", x = "Environmental effect direction", fill = "Count") + 
  geom_text(aes(label = n)) + 
  scale_fill_gradient(low = "#FEE08B", high = "#D53E4F") +
  guides(fill = "none")

Fig7h
```

### Fig. 7 - Panel

```{r fig7panel, fig.width=15, fig.height=20}

Fig7 <- ((Fig7a | Fig7b) /(Fig7c | Fig7d) / (Fig7e | Fig7f) / (Fig7g | Fig7h)) + plot_annotation(tag_levels = "A")

Fig7

#Exported PDF as 20 x 15 inch
```

# Objective Three

## Figure 8 - Countries {.tabset}

### Fig. 8A  - Map

```{r fig8a, echo = FALSE, results = 'hide'}
## Figure X - Country of first author  affiliation - map
#https://www.riinu.me/2022/02/world-map-ggplot2/
#table(bib2$AU1_CO) #column with countries of first authors

bib2 <- metaTagExtraction(bib, Field = "AU1_CO", sep = ";") 
bib2 <- metaTagExtraction(bib2, Field = "AU_CO", sep = ";") 

#save counts in a data frame
bib2 %>% group_by(AU1_CO) %>% count() %>% filter(!is.na(AU1_CO)) -> firstcountrycounts

#load map data
world_map <- map_data("world") %>% 
  filter(! long > 180) #remove countries with longitude >180 to make equal projection-like map without artifacts
#table(world_map$region) #note that United Kingdom is UK here

# Format country names to match regions on the world map
firstcountrycounts$region <- str_to_title(firstcountrycounts$AU1_CO)
firstcountrycounts$region[firstcountrycounts$region == "Usa"] <- "USA" #Fix "Usa" to "USA" :
firstcountrycounts$region[firstcountrycounts$region == "United Kingdom"] <- "UK" #fix to "UK"
#(firstcountrycounts$region) %in% world_map$region #check matching

## colour all regions on the map:
emptymap <- tibble(region = unique(world_map$region), n = rep(0,length(unique(world_map$region)))) #create table with all counts as 0
fullmap <- left_join(emptymap, firstcountrycounts, by = "region") #join with actual counts table
fullmap$n <- fullmap$n.x + fullmap$n.y # make new column for fixed counts
fullmap$n[is.na(fullmap$n)] <- 0 #change NA to 0 for regions with no counts

Fig8a <- fullmap %>% 
  ggplot(aes(fill = n, map_id = region)) +
  geom_map(map = world_map) +
  expand_limits(x = world_map$long, y = world_map$lat) +
  coord_map("moll") +
  theme_map(line_size = 0.5) + 
  theme(legend.position="right") +
  scale_fill_gradient(low = "#FEE08B", high = "#D53E4F",
 limits = c(1, 12),
      guide = guide_colorbar(direction = "vertical.")) +
  guides(fill = guide_colourbar(barwidth = unit(15, units = "mm"), barheight = unit(20, units = "mm")))

Fig8a
```

### Fig. 8B - Country collaborations

```{r fig8b, echo = FALSE, results = 'hide'}

NetMatrix2 <- biblioNetwork(bib2, analysis = "collaboration", 
                           network = "countries", sep = ";")

net_matrix2 <- as.matrix(NetMatrix2)
#net_matrix2 <-net_matrix[rownames(NetMatrix2), countries]
diag(net_matrix2) <- 0 #get rid of collaboration with same country

# net_matrix2

# getting rid of lower triangle (as this is duplication of info)
net_matrix2[lower.tri(net_matrix2)] <- 0 
#colnames(net_matrix2) - change to title case:
colnames(net_matrix2) <- str_to_title(colnames(net_matrix2))
#rownames(net_matrix2) - change to title case:
rownames(net_matrix2) <- str_to_title(rownames(net_matrix2))
#Fix "Usa" to "USA" :
colnames(net_matrix2)[colnames(net_matrix2) == "Usa"] <- "USA"
rownames(net_matrix2)[rownames(net_matrix2) == "Usa"] <- "USA"
#change "UNITED KINGDOM" to "UK" for easier plotting:
colnames(net_matrix2)[colnames(net_matrix2) == "United Kingdom"] <- "UK"
rownames(net_matrix2)[rownames(net_matrix2) == "United Kingdom"] <- "UK"

colnames(net_matrix2)[7] <- "Newzealand" 
rownames(net_matrix2)[7] <- "Newzealand"

circos.clear()
my.cols2 <- c(USA = "#DCDCDC", Australia = "#000000", Netherlands = "#A9A9A9", UK = "#2F4F4F", Brazil = "#C0C0C0", Canada = "slategray", Newzealand = "gainsboro", France = "#778899", Germany = "#808080",Italy = "#696969", Argentina = "#DCDCDC", China = "#000000", Belgium = "#A9A9A9", Sweden = "#2F4F4F", Iran = "#C0C0C0", Mexico = "#778899", Poland = "#A9A9A9")


Fig8b <- chordDiagram(net_matrix2, annotationTrack = "grid", preAllocateTracks = 1, grid.col = my.cols2)

circos.trackPlotRegion(track.index = 1, panel.fun = function(x, y) {
  xlim = get.cell.meta.data("xlim")
  ylim = get.cell.meta.data("ylim")
  sector.name = get.cell.meta.data("sector.index")
  circos.text(mean(xlim), ylim[1] + .1, sector.name, facing = "clockwise", niceFacing = TRUE, adj = c(0, 0.5))
  circos.axis(h = "top", labels.cex = 0.5, major.tick.percentage = 0.2, sector.index = sector.name, track.index = 2)
}, bg.border = NA)


Fig8b

#TODO may need to change shade of grey for USA
```

### Panel
Saving panel as a PDF

```{r fig8panel, eval = FALSE}
pdf(file = "Countries.pdf", width = 8, height = 10)

# layout(matrix(1:2, 1, 2))
par(mfrow = c(2, 1), mar = c(0.5, 0.5, 0.9, 0.5), bg = rgb(1, 1, 1, 0.1) , adj = 0, cex = 1.1)

fullmap %>% 
  ggplot(aes(fill = n, map_id = region)) +
  geom_map(map = world_map) +
  expand_limits(x = world_map$long, y = world_map$lat) +
  coord_map("moll") +
  theme_map(line_size = 0.5) + 
  theme(legend.position="right") +
  scale_fill_gradient(low = "#FEE08B", high = "#D53E4F",
 limits = c(1, 12),
      guide = guide_colorbar(direction = "vertical.")) +
  guides(fill = guide_colourbar(barwidth = unit(15, units = "mm"), barheight = unit(20, units = "mm"))) +
  ggtitle("A")
         
         
circos.clear()
circos.par(start.degree = 90)
circos.par("circle.margin" = c(0.1, 0.1, 0.5, 0.1))
fig1 <- chordDiagram(net_matrix2, annotationTrack = "grid", preAllocateTracks = 1, grid.col = my.cols2)
#change direction of labels
circos.trackPlotRegion(track.index = 1, panel.fun = function(x, y) {
  xlim = get.cell.meta.data("xlim")
  ylim = get.cell.meta.data("ylim")
  sector.name = get.cell.meta.data("sector.index")
  circos.text(mean(xlim), ylim[1] + .3, sector.name, facing = "clockwise", niceFacing = TRUE, adj = c(0, 0.5))
  circos.axis(h = "top", labels.cex = 0.3, major.tick.percentage = 0.2, sector.index = sector.name, track.index = 2)
}, bg.border = NA)
title("B", font.main = 1, cex.main = 1.2)
dev.off()
```

## Figure 9 - Collaborations

```{r fig9, results='hide'}
# Data
Publication_info_discipline <- merge(Publication_info, Review_info)

# matching with 1st author and title
# mapping data
Fields <- Publication_info_discipline %>%
  mutate(title = tolower(unlist(lapply(data.frame(t(str_split_fixed(title, " ", n = 15)[,1:14])), 
                                       function(x) str_c(x, collapse  = " ")))),
         ntitle = paste(tolower(str_split_fixed(id, "\\_", n = 2)[,1]), title, sep = " "),
         ntitle = trimws(ntitle)) %>% 
  select(ntitle, discipline_code)

# bib data
Bib_names <- bib %>% rownames_to_column(., var = "mat_names") %>% 
  mutate(TI2 = tolower(unlist(lapply(data.frame(t(str_split_fixed(TI, " ", n = 15)[,1:14])), 
                                     function(x) str_c(x, collapse  = " ")))),
         # stri_trans_general = getting rid of special letters
         name2 = stri_trans_general(tolower(str_split_fixed(SR, " ", n = 2)[,1]), "latin-ascii"),
         TI2 = paste(name2, TI2, sep= " "),
         TI2 = trimws(TI2)) %>% 
  select(TI2, mat_names)
 
#stringdist(Bib_names$TI2, Fields$ntitle[1], method = 'osa')
pos <- lapply(Bib_names$TI2, function(x) stringdist(Fields$ntitle, x))
pos2<- map_dbl(pos, which.min)

# these are looking good - both have the perfect matches (at least at a glance)
Bib_names$TI2
Fields$ntitle[pos2]

# now we can merge two datasets 
Bib_names$discipline_code <- Fields$discipline_code[pos2]

# Creating matrix for bibliometric coupling
NetMatrix <- biblioNetwork(bib, analysis = "coupling", network = "references", sep = ";")

# forcing into a nromal matrix
net_matrix <- as.matrix(NetMatrix)
diag(net_matrix) <- 0 #get rid of counts for the same papers

# replacing names with discipline_code
rownames(net_matrix) <- Bib_names$discipline_code
colnames(net_matrix) <- Bib_names$discipline_code

# reducing matrix according to discipline_code
rect_matrix<- t(rowsum(t(net_matrix), group = colnames(net_matrix), na.rm = T))
small_matrix <- rowsum(rect_matrix, group = rownames(rect_matrix))

# getting rid of lower triangle (as this is duplication of info)
small_matrix[lower.tri(small_matrix)] <- 0 


# small_matrix - for getting percents
#percent of shared citations with other disciplines
#eco evo
# (25 + 97 + 31) / (25 + 97 + 31 + 206)

#cross-disciplinary
# (39+2) / (39+2+8)

#toxicology
# (2+2+3 +1) / (2+2+3+1+42)

#biomed
# (39 + 97 + 2) / (39 + 97 + 2 + 616)

#agriculture
# (25 + 2 + 25 + 3) / (25 + 2 + 25 + 3 + 48)

#have to remove gaps and hyphen to allocate colours to match previous figures
colnames(small_matrix)[3] <- "crossdisciplinary"
colnames(small_matrix)[4] <- "ecoevo"
rownames(small_matrix)[3] <- "crossdisciplinary"
rownames(small_matrix)[4] <- "ecoevo"


my.cols <- (c(agriculture = "#66C2A5", biomed = "#FC8D62", crossdisciplinary = "#8DA0CB", ecoevo = "#E78AC3", toxicology = "#A6D854"))
            
par(mar = c(0, 0, 0, 0), mfrow = c(1, 1))

# chord diagram
circos.par()
Fig9 <- chordDiagramFromMatrix(small_matrix, grid.col = my.cols)
Fig9

#TODO manually add spaces and hyphens in discipline names
#Exported pdf as 7 x 4 inches

```

# Objective Four

```{r ceesat}
#blinding authors
Assessment$id <- paste("ID", c(1:length(Assessment$id)), sep = "")
#shortening column names
names(Assessment) <- gsub("CEESAT_", "", names(Assessment), fixed = TRUE)
#selecting only the columns with scores
#selecting only the columns with scores
Assessment_reduced <- select(Assessment, c("id", !ends_with("_comment")))
#wrangling data into long format
ceesat_long <- gather(Assessment_reduced, question, score, Q1.1:Q8.1, factor_key=TRUE)
```

## Figure 10 

```{r fig10}
#calculating the % of scores within each questions 
count_ceesat_score <- ceesat_long %>% count(score, by = question) 
percent_ceesat_score <- count_ceesat_score %>% mutate(percent = (n/sum(n))*100)
percent_ceesat_score <- percent_ceesat_score %>%
  rename(
    question = by
  )
percent_ceesat_score$question <- as.factor(percent_ceesat_score$question)
percent_ceesat_score$question <- factor(percent_ceesat_score$question, levels(percent_ceesat_score$question)[length(percent_ceesat_score$question):1]) #reverse the order of questions
percent_ceesat_score$score <- as.factor(percent_ceesat_score$score)
percent_ceesat_score$score <- factor(percent_ceesat_score$score, levels(percent_ceesat_score$score)[c(2,3,1,4)]) #set the order of levels for assessment scores:

Fig10 <- ggplot(data = percent_ceesat_score, x = question, y = percent) +
  geom_col(mapping = aes(x = question, y = percent, fill = score), width = 0.7,
           position = "fill", color = "black") +
  coord_flip(ylim = c(0, 1)) +
  guides(fill = guide_legend(reverse = TRUE)) +
  scale_fill_manual(values = c("yellow","green", "orange","red"), name = "Score:") +
  theme(legend.position = "none", panel.grid.major = element_blank(),panel.grid.minor = element_blank(),panel.background = element_blank()) + 
  ylab("Proportion") + xlab("CEESAT Question")

Fig10

#Exported as PDF 5 x 7 inches
``` 
