---
title: "Main text figures: Objectives one and two"
author: "Erin Macartney, Szymek Drobniak, Shinichi Nakagawa, Malgorzata Lagisz"
output:
    rmdformats::readthedown:
      code_folding: hide
      code_download: true
      toc_depth: 4
editor_options:
  chunk_output_type: console
---

    
```{r, include = FALSE}
knitr::opts_chunk$set(
message = FALSE,
warning = FALSE,
cache = FALSE,
tidy = TRUE,
echo = TRUE
)

rm(list = ls())
```

### Setup and data organisation

```{r setup, results = 'hide'}

knitr::opts_chunk$set(echo = TRUE)

library(readxl)
library(plyr)
library(here)
library(tibble)
library(dplyr)
library(tidyverse)
library(stringr)
library(knitr)
library(forcats)
library(ggplot2)
library(hrbrthemes) #for ggplot2
library(bibliometrix)
library(igraph)
library(patchwork)
library(RColorBrewer)
library(wordcloud2)
library(migest)
library(circlize)
```

``` {r, results = 'hide'}
#manually extracted data
xldata <- "./data/Data_extraction_postcrosschecking.xlsx"

# xldata <- read_excel(here("data", "Data_extraction_postcrosschecking.xlsx"))
#note that here packeage doen't work with data wrangling code below

# #bibliometric data
# bib <- convert2df("./data/bibliometric.bib", dbsource = "scopus", format = "bibtex")
# 
# bib <- convert2df(here("data", "bibliometric.bib"), dbsource = "scopus", format = "bibtex")
```

``` {r, results = 'hide'}
#Splitting list of tabs into separate dataframes
excel_sheets(path = xldata)
tab_names <- excel_sheets(path = xldata)


#creating a list of dataframes per tab
list_all <- lapply(tab_names, function(x) read_excel(path = xldata, sheet = x))

#assigning tab names to each dataframe
names(list_all) <- tab_names

#get dataframes out of list
list2env(list_all, .GlobalEnv)
```

# Objective One - Between discipline patterns 

## Figure 3  

### Fig 3A - Time trend

``` {r}

Publication_info_discipline <- merge(Publication_info, Review_info)

Fig3a <- Publication_info_discipline %>% 
  count(year) %>%
  ggplot(aes(x = year, y = n)) +
  geom_col(aes(), width = 0.7) +
  xlim(2009, 2021.5) +
  ylim(0, 14.5) +
  geom_text(aes(label = n),vjust = -0.2) +
  theme_classic() +
  labs(x = "Year", y = "Article count")+
  theme(legend.position = "none", axis.title.x = element_text(size = 10))

Fig3a

```

## Figure 4  
Species

## Figure 5  {.tabset}

### Fig. 5A - Inter- vs trans- inheritance

``` {r}
count_inter_vs_trans <- count(Inter_vs_trans_info, inter_vs_trans_code)
percent_inter_vs_trans <- count_inter_vs_trans %>% mutate(percent = (n/sum(n))*100)

percent_inter_vs_trans$percent <- round(percent_inter_vs_trans$percent, digits = 0)

Fig5a <- ggplot(percent_inter_vs_trans, aes(x = inter_vs_trans_code, y = percent)) +
  geom_col(aes(), width = 0.7) +
  coord_flip() + 
  labs(y = "Percent (%)") +
  ylim(0,100)+
  geom_text(aes(label = percent), hjust = -0.2) +
  theme_classic() +
  labs(x = "Inter- vs trans-inheritnace")

Fig5a
```

### Fig. 5B - Terminology match vs mismatch

```{r}

count_terminology <- count(Review_info, terminology_code)
percent_terminology <- count_terminology %>% mutate(percent = (n/sum(n))*100)

percent_terminology$percent <- round(percent_terminology$percent, digits = 0)

Fig5b <- ggplot(percent_terminology, aes(x =reorder(terminology_code, -percent), y = percent)) + 
  coord_flip() + 
  geom_col(aes(), width = 0.7) + 
  labs(y = "Percent (%)",x = "Terminology use matches Fig. 1" ) +
  ylim(0,100) +
  geom_text(aes(label = percent), hjust = -0.2)+
  theme_classic()


Fig5b

```

### Fig. 5C - Type of F0 exposure

```{r}

count_F0_env <- count(F0_env_info, F0_env_code)
percent_F0_env <- count_F0_env %>% mutate(percent = (n/sum(n))*100)

percent_F0_env$percent <- round(percent_F0_env$percent, digits = 0)

Fig5c <- ggplot(percent_F0_env, aes(x = reorder(F0_env_code, -percent), y = percent)) + 
  geom_col(aes(), width = 0.7) +
  coord_flip() + 
  labs(y = "Percent (%)",x = "Type of environmental exposure" ) +
  ylim(0,100) +
  geom_text(aes(label = percent), hjust = -0.2)+
  theme_classic()
  
Fig5c
```

### Fig. 5D - Transmission mode 

```{r}

count_transmission <- count(Transmission_info, transmission_code)
percent_transmission <- count_transmission %>% mutate(percent = (n/sum(n))*100)

percent_transmission$percent <- round(percent_transmission$percent, digits = 0)

Fig5d <- ggplot(percent_transmission, aes(x = reorder(transmission_code, -percent), y = percent)) + 
  geom_col(aes(), width = 0.7) +
  coord_flip() + 
  labs(y = "Percent (%)") +
  ylim(0,100) +
  geom_text(aes(label = percent), hjust = -0.2)+
  theme_classic() +
  labs(x = "Transmission mode")

Fig5d

```

### Fig. 5E - Timing of F0 exposure

```{r}

count_exposure_timing <- count(Exposure_timing_info, exposure_timing_code)
percent_exposure_timing <- count_exposure_timing %>% mutate(percent = (n/sum(n))*100)

percent_exposure_timing$percent <- round(percent_exposure_timing$percent, digits = 0)

Fig5e<- ggplot(percent_exposure_timing, aes(x = reorder(exposure_timing_code, -percent), y = percent)) + 
  geom_col(aes(), width = 0.7) + 
   coord_flip() + 
  labs(y = "Percent (%)",x = "Timing of F0 (ancestor) exposure" ) +
  ylim(0,100) +
  geom_text(aes(label = percent), hjust = -0.2)+
  theme_classic()

Fig5e
```

### Fig. 5F - Descendant trait

```{r}
count_descendant_trait <- count(Descendant_trait_info, descendant_trait_code)
percent_descendant_trait <- count_descendant_trait%>% mutate(percent = (n/sum(n))*100)
percent_descendant_trait$percent <- round(percent_descendant_trait$percent, digits = 0)


Fig5f<- ggplot(percent_descendant_trait, aes(x = reorder(descendant_trait_code, -percent), y = percent)) + 
  geom_col(aes(), width = 0.7) + 
  coord_flip() + 
  labs(y = "Percent (%)",x = "Descendant traits" ) +
  ylim(0,100) +
  geom_text(aes(label = percent), hjust = -0.2)+
  theme_classic()

Fig5f
```

### Fig. 5G - Descendant sex

```{r}

count_descendant_sex <- count(Descendant_sex_info, descendant_sex_code)
percent_descendant_sex <- count_descendant_sex%>% mutate(percent = (n/sum(n))*100)
percent_descendant_sex$percent <- round(percent_descendant_sex$percent, digits = 0)


Fig5g <- ggplot(percent_descendant_sex, aes(x = reorder(descendant_sex_code, -percent), y = percent)) + 
  geom_col(aes(), width = 0.7) + 
  coord_flip() + 
  labs(y = "Percent (%)",x = "Descendant sex" ) +
  ylim(0,100) +
  geom_text(aes(label = percent), hjust = -0.2)+
  theme_classic()

Fig5g

```

### Fig. 5H - Environmental effect direction 

```{r}

count_env_eff <- count(Env_eff_diection_info, env_eff_direction_code)
percent_env_eff <- count_env_eff%>% mutate(percent = (n/sum(n))*100)
percent_env_eff$percent <- round(percent_env_eff$percent, digits = 0)


Fig5h <- ggplot(percent_env_eff, aes(x = reorder(env_eff_direction_code, -percent), y = percent)) + 
  geom_col(aes(), width = 0.7) + 
  coord_flip() +
  labs(y = "Percent (%)",x = "Environmental effect direction" ) +
  ylim(0,100) +
  geom_text(aes(label = percent), hjust = -0.2)+
  theme_classic()
  
Fig5h

```

### Fig. 5 - Panel 

```{r}
Fig5 <- ((Fig5a | Fig5b) / (Fig5c | Fig5d) / (Fig5e | Fig5f) / (Fig5g | Fig5h)) + plot_annotation(tag_levels = "A")

Fig5

```

#Objective Two - Within discipline effects

## Figure 6 {.tabset}

### Fig. 6A - Percent SRs within disciplines

``` {r, results = 'hide'}

count_discipline <-Review_info %>% count(discipline_code)
# %>% arrange(desc(n)) 
percent_discipline <- count_discipline %>% mutate(percent = (n/sum(n))*100)
percent_discipline$percent <- round(percent_discipline$percent, digits = 0)
# percent_discipline$discipline_code <- factor(percent_discipline$discipline_code, level = percent_discipline$discipline_code[order(percent_discipline$n, decreasing = TRUE)])

brewer.pal(6, "Set2")
my.cols <- (c("#66C2A5", "#FC8D62", "#8DA0CB", "#E78AC3", "#A6D854", "#FFD92F"))

Fig6a <- ggplot(percent_discipline, aes(x = discipline_code, y = percent)) + 
  geom_col(aes(fill = discipline_code)) + 
  geom_text(aes(label = percent), vjust = -0.2) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(name = "Percent (%)") +
  xlab("Discipline") + 
  scale_fill_manual(values=my.cols) +
  theme_classic() +
  theme(legend.position = "none")

Fig6a

```



### Fig. 6B - Disciplines within taxa

``` {r}
Merged_taxa <- merge(Species_info, Review_info)
#creating a subset dataframe without repreated measures of taxa per species
Merged_taxa2 <- Merged_taxa[c("id", "broad_taxa", "discipline_code")]
Merged_taxa3 <- Merged_taxa2 %>% distinct(id, broad_taxa,.keep_all = TRUE)

count_taxa <- Merged_taxa3 %>% count(broad_taxa, by = discipline_code ) %>% arrange(desc(n))


count_taxa <-count_taxa%>%
  rename(
    discipline_code = by
  )

Fig6b <- ggplot(count_taxa, aes(x = fct_rev(broad_taxa), y = n, fill = discipline_code)) +
  geom_bar(position = "fill", stat = "identity") + 
  theme_classic() +
  coord_flip() +
  labs(y = "Proportion", x = "Broad taxa", fill = "Discipline") +
  scale_fill_brewer(palette = "Set2") +
  theme(legend.position = "none")

Fig6b
```

### Fig. 6 - Panel

```{r}
Fig6 <- (Fig6a + Fig6b) + plot_annotation(tag_levels = "A")

Fig6

```

## Figure 7 {.tabset}

### Fig. 7A - Inter- vs trans- inheritance

``` {r}
Merged_inter_vs_trans <- merge(Inter_vs_trans_info, Review_info)

count_inter_vs_trans <- Merged_inter_vs_trans %>% count(inter_vs_trans_code, by = discipline_code ) %>% arrange(desc(n))

count_inter_vs_trans <-count_inter_vs_trans %>%
  rename(
    discipline_code = by
  )

Fig7a <- ggplot(count_inter_vs_trans, aes(y = discipline_code, x = inter_vs_trans_code, fill = n)) +
  geom_raster() + 
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Discipline", x = "Inter- vs trans-inheritance", fill = "Count") + 
  geom_text(aes(label = n)) + 
  scale_fill_gradient(low = "#FEE08B", high = "#D53E4F") +
  guides(fill = "none")

Fig7a
```

### Fig. 7B - Terminology match vs mismatch

``` {r}
count_terminology <- Review_info %>% count(terminology_code, by = discipline_code) %>% arrange(desc(n))

count_terminology<- count_terminology %>%
  rename(
    discipline_code = by
  )

Fig7b <- ggplot(count_terminology, aes(x = reorder(terminology_code, -n), y = discipline_code, fill = n)) +
  geom_raster() + 
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Discipline", x = "Terminology use matches Fig. 1", fill = "Count") + 
  geom_text(aes(label = n)) + 
  scale_fill_gradient(low = "#FEE08B", high = "#D53E4F") +
  guides(fill = "none")

Fig7b

```

### Fig. 7C - Type of F0 exposure

```{r}

merged_F0_env <- merge(F0_env_info, Review_info)
count_F0_env<- merged_F0_env %>% count(F0_env_code, by = discipline_code ) %>% arrange(desc(n))
 
count_F0_env <-count_F0_env %>%
  rename(
    discipline_code = by
  )

Fig7c <- ggplot(count_F0_env, aes(y = discipline_code, x = F0_env_code, fill = n)) +
  geom_raster() + 
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Discipline", x = "Type of environmental exposure", fill = "Count") + 
  geom_text(aes(label = n)) + 
  scale_fill_gradient(low = "#FEE08B", high = "#D53E4F") +
  guides(fill = "none")

Fig7c
```


### Fig. 7D - Transmission mode

```{r}
Merged_transmission_info <- merge(Transmission_info, Review_info)

count_transmission <- Merged_transmission_info %>%  count(transmission_code, by = discipline_code) %>% arrange(desc(n))

count_transmission <-count_transmission %>%
  rename(
    discipline_code = by
  )


Fig7d <- ggplot(count_transmission, aes(y = discipline_code, x = transmission_code, fill = n)) +
  geom_raster() + 
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Discipline", x = "Transmission mode", fill = "Count") + 
  geom_text(aes(label = n)) + 
  scale_fill_gradient(low = "#FEE08B", high = "#D53E4F") +
  guides(fill = "none")

Fig7d

```

### Fig. 7E - Timing of F0 Exposure

```{r}

merged_exposure_timing <- merge(Exposure_timing_info, Review_info)

count_exposure_timing <- merged_exposure_timing %>% count(exposure_timing_code, by = discipline_code) %>% arrange(desc(n))

count_exposure_timing <- count_exposure_timing %>%
  rename (
    discipline_code = by
  )

Fig7e <- ggplot(count_exposure_timing, aes(y = discipline_code, x = exposure_timing_code, fill = n)) +
  geom_raster() + 
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Discipline", x = "Timing of F0 (ancestor) exposure", fill = "Count") + 
  geom_text(aes(label = n)) + 
  scale_fill_gradient(low = "#FEE08B", high = "#D53E4F") +
  guides(fill = "none")

Fig7e
```

### Fig. 7F - Descendant trait

```{r}

merged_descendant_trait <- merge(Descendant_trait_info, Review_info)
count_descendant_trait <- merged_descendant_trait %>% count(descendant_trait_code, by = discipline_code) %>% arrange(desc(n))

count_descendant_trait <- count_descendant_trait %>%
  rename(
    discipline_code = by
  )

Fig7f <- ggplot(count_descendant_trait, aes(y = discipline_code, x = descendant_trait_code, fill = n)) +
  geom_raster() + 
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Discipline", x = "Descendant traits", fill = "Count") + 
  geom_text(aes(label = n)) + 
  scale_fill_gradient(low = "#FEE08B", high = "#D53E4F") +
  guides(fill = "none")

Fig7f
```

### Fig. 7G - Descendant sex

```{r}

merged_descendant_sex <- merge(Descendant_sex_info, Review_info)
count_descendant_sex <- merged_descendant_sex %>% count(descendant_sex_code, by = discipline_code) %>% arrange(desc(n))

count_descendant_sex <- count_descendant_sex %>%
  rename(
    discipline_code = by
           )

Fig7g <- ggplot(count_descendant_sex, aes(y = discipline_code, x = descendant_sex_code, fill = n)) +
  geom_raster() + 
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Discipline", x = "Descendant sex", fill = "Count") + 
  geom_text(aes(label = n)) + 
  scale_fill_gradient(low = "#FEE08B", high = "#D53E4F") +
  guides(fill = "none")

Fig7g
```

### Fig. 7H - Environmental effect direction 

```{r}

merged_env_eff <- merge(Env_eff_diection_info, Review_info)

count_env_eff <- merged_env_eff %>% count(env_eff_direction_code, by = discipline_code) %>% arrange(desc(n))

count_env_eff <-count_env_eff %>%
  rename(
    discipline_code = by
  )

Fig7h <- ggplot(count_env_eff, aes(y = discipline_code, x = env_eff_direction_code, fill = n)) +
  geom_raster() + 
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Discipline", x = "Environmental effect direction", fill = "Count") + 
  geom_text(aes(label = n)) + 
  scale_fill_gradient(low = "#FEE08B", high = "#D53E4F") +
  guides(fill = "none")

Fig7h
```

### Fig. 7 - Panel

```{r}

Fig7 <- ((Fig7a | Fig7b) /(Fig7c | Fig7d) / (Fig7e | Fig7f) / (Fig7g | Fig7h)) + plot_annotation(tag_levels = "A")

Fig7
```
